---
title: "The Life Event Survey Tool"
author: "David A York"
date: "January 16, 2016"
output: slidy_presentation
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
# demo data file load
demoData <<- read.csv("dataJan-21-2016.csv",colClasses=c("integer","character","character","character","factor", "integer"))

factScore = c(rep(" ", length(demoData[,6])))
for (i in seq(1:length(demoData$score))){if (demoData[i,6] > 150) {factScore[i] <- "high"}
      else{factScore[i] <- "low"}}
demoData <- mutate(demoData, riskGroup=as.factor(factScore))


##Dummy Survey Data Creation Maintenance

# create df
  illnessSurvey <- as.data.frame(matrix(data=c("fld1","Fld2","fld3", "fld4","fld5","fld6"),nrow=1,
                                        byrow=TRUE))
  colnames(illnessSurvey) <- c("refNo","collectDate", "subjEmail","cenTract","ageRange","score")
# change all to character
  for (i in seq(1:6) ) {
    illnessSurvey[,i] <- as.character(illnessSurvey[,i])
  }
# make first line proper format dummy data
  illnessSurvey[1,] <- list("1000000","2016-01-31","dummy0@gmail.com","50218","65","150")
# change collectDate tp data class
  illnessSurvey$collectDate <-as.Date(illnessSurvey$collectDate)
# change score to integer
  illnessSurvey$score <-as.integer(illnessSurvey$score)
# add data with age range
  illnessSurvey[2,] <- list("1000001","2016-01-31","dummy1@gmail.com","02005","17",100)
  illnessSurvey[3,] <- list("1000002","2016-01-31","dummy2@gmail.com","04105","20",100)
  illnessSurvey[4,] <- list("1000003","2016-01-31","dummy3@gmail.com","08805","30",300)
  illnessSurvey[5,] <- list("1000004","2016-01-31","dummy4@gmail.com","12305","40",60)
  illnessSurvey[6,] <- list("1000005","2016-01-31","dummy5@gmail.com","45304","50",250)
  illnessSurvey[7,] <- list("1000006","2016-01-31","dummy6@gmail.com","82614","60",100)
  illnessSurvey[8,] <- list("1000007","2016-01-31","dummy7@gmail.com","98014","65",200)
  illnessSurvey[9,] <- list("1000008","2016-01-31","dummy8@gmail.com","71030","65",200)

#factorize ageRange with proper levels
  illnessSurvey$ageRange <- as.factor(illnessSurvey$ageRange)
  
  
  
# create a map plot score by zip 
  library(choroplethrZip)
  df <- as.data.frame(cbind(as.character(demoData$cenTract),as.factor(demoData$riskGroup)),stringsAsFactors=FALSE)
  colnames(df) <- c("region", "value")
  df$value <- as.integer(df$value)
  # summarize to mean value per region (zip/cenTract)
  aggData <- summarise(group_by(df, region), round(mean(value)))
  colnames(aggData) <- c("region","value")
  regionScore <- zip_choropleth(aggData, title = "Score by region", num_colors = 2)

```

## The Investment

The Project intends to provide both a client friendly data collection platform and a tool for database maintenance, manipulation and analysis.

- The Client-user facing part is a clear and simple survey taker and feedback application
- The How-tos for both client-user and investigator-user are concise and complete and integrated smoothly with the tool
- The complete tool collects, provides client feed back and outcome follow-up. As well the collected data are stored in simple comma-separated format which can be sent to the investigator site for study.
- simple view and analysis of the insitu data is provided by the tool and it's integrity can be assured.


## The Tool

- a free open source solution
- The tool is a complete data input, storage, analysis and maintenance application.
- The tool is secure when deployed,
  - zipcodes are converted immediately to census tract codes before storing
  - potential identifying data are encrypted
  - data can only be sent to a preselected addresses

**Database Excerpt**
```{r echo=FALSE}
knitr::kable(demoData[c(1:5),c(2:6)], col.names=c("Date","email","Tract","Age Group","Score"))
```




## Simple Reports - Tables
<br><br>
**Summary**
<br>
```{r echo=FALSE}
knitr::kable(summary(demoData[,c(5,6)]))
```




## Simple Reports - Plots
<br>
<center>
Plot Age Group versus Score
<br>
```{r echo=FALSE}
regionScore
```




## The Payoff

- simple, free, open-source solution to hosting the survey
- Client-users have an easy survey to complete with immediate risk feedback as reward
- Survey collected unattended, 24x7
- Secure and confidential
- The application communicates, on demand, with the investigator, off site, to allow more complex analysis, presentation and ultimate publication.

